Mossy Pond mrmr model 1

### 2024-11-22 code/R/MossyPond_Classic_mrmr.Rmd
update fit_model_classic function and change object names

# clean data 
mrmr_mossy_mod1_data <- clean_data(captures, surveys)

# fit classic mrmr model
mrmr_mossy_mod1 <- fit_model(mrmr_mossy_mod1_data,
                                chains = 3, 
                                iter_sampling = 1000, 
                                iter_warmup = 400)

# save model summary to an object
mod1_summary <- mrmr_mossy_mod1$m_fit$summary()
view(mod1_summary)

write.csv(mod1_summary, "/Users/johnimperato/Desktop/Mossy-Pond_companion/mp_classic_mod_sumary.csv")

>>>>

# clean data 
mp_data <- clean_data(captures, surveys)

# load fit_model_classic function
source("classic_fit_model_function.R")

# fit classic mrmr model
classic_mod_mp <- fit_model_classic(mp_data,
                                chains = 3, 
                                iter_sampling = 1000, 
                                iter_warmup = 400)

# save model summary to an object
classic_mod_mp_summary <- classic_mod_mp$m_fit$summary()
View(classic_mod_mp_summary)

write.csv(classic_mod_mp_summary, "/Users/johnimperato/Desktop/Mossy-Pond_companion/mp_classic_mod_sumary.csv")
